### 2016-11-16 src/local.tex
going home

>>>>

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm, 
define the following graph $L = (\{v_i : s_i \in M^* \}, E)$ 
where $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
That is, each vertex in $L$ corresponds to a star in $M^*$ and there is an edge 
between two vertices if and only if there is an edge $(u,v)$ in $M$ connecting the two 
corresponded stars.
Denote by $d^*_i$ the sum of the degrees in $s_i$, and by $d_i$ the sum of the degrees of 
edges from $M$ intersected with $s_i$. \todo{better define this last line}
\todo{add an illustration}
